BDP draft paper

### 2016-08-03 final_paper/draft.Rmd
draft paper

 For the final project, our group cleaned, explored, and analyzed four different data sets from the City of Berkeley that contained information on stops, calls for service, arrests, and jail bookings made by the the police department in 2016 (and 2015 as well for the stop data). Rather than limiting the project to one set of data, four sets were chosen in order to gain a more holistic and comprehensive understanding of the data. The additional variables included expanded the project’s capacity for manipulating data, examining relationships, and improving result reliability.

@@

* [Stop Data (16,000)](https://data.cityofberkeley.info/Public-Safety/Berkeley-PD-Stop-Data/6e9j-pj9p)
* [Arrest (200)](https://data.cityofberkeley.info/Public-Safety/Berkeley-PD-Log-Arrests/xi7q-nji6)
* [Jail Bookings (250)](https://data.cityofberkeley.info/Public-Safety/Berkeley-PD-Log-Jail-Bookings/7ykt-c32j)
* [Calls for Service (4,000)](https://data.cityofberkeley.info/Public-Safety/Berkeley-PD-Calls-for-Service/k2nh-s5h5)
* [Berkeley Census Data](https://data.cityofberkeley.info/)

@@

	The calls for service data (4913 offenses) contained information on the case number, the offense type with a description of said offense, the date and start and end time for each case and the date of case entry into the database, and the location. Because the data set contained little to no information on the subjects apprehended in each case, it was largely used for mapping purposes.

>>>>

 For the final project, our group cleaned, explored, and analyzed four different data sets from the City of Berkeley that contained information on stops, calls for service, arrests, and jail bookings made by the the police department in 2016 (and 2015 as well for the stop data). Rather than limiting the project to one set of data, three sets were chosen in order to gain a more holistic and comprehensive understanding of the data. The additional variables included expanded the project’s capacity for manipulating data, examining relationships, and improving result reliability.

@@

* [Stop Data (16,000)](https://data.cityofberkeley.info/Public-Safety/Berkeley-PD-Stop-Data/6e9j-pj9p)
* [Arrest (200)](https://data.cityofberkeley.info/Public-Safety/Berkeley-PD-Log-Arrests/xi7q-nji6)
* [Jail Bookings (250)](https://data.cityofberkeley.info/Public-Safety/Berkeley-PD-Log-Jail-Bookings/7ykt-c32j)
* [Berkeley Census Data](https://data.cityofberkeley.info/)

@@
